---
title: "Dunnart peak characterisation"
author: "lecook"
date: "2022-02-23"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# Introduction
This analysis looks through various features of the dunnart peaks including peak intensity, lengths, distance to TSS and nearest gene calls.


# Load libraries
```{r}
library(GenomicFeatures)
library(GenomicRanges)
library(rtracklayer)
library(AnnotationForge)
library(clusterProfiler)
library(ChIPseeker)
library(ggpubr)
library(AnnotationDbi)
library(AnnotationHub)
library(org.Mm.eg.db)
library(plyr)
library(tidyverse)
library(RColorBrewer)
library(ggplot2)
library(data.table)
library(ggridges)
library(reshape2)
library(RColorBrewer)
library(VennDiagram)
library(viridis)
library(hrbrthemes)
library(gghalves)
library(multcompView)
library(factoextra)
library(NbClust)
```

# Set up 
Set fonts, plot and output directories etc.

```{r}
setwd("/data/projects/punim0586/lecook/chipseq-cross-species/output/")
plot_dir = "plots/"
fullPeak_dir = "peaks/"
annot_dir = "annotations/"
filterPeaks_dir = "filtered_peaks/"

## Set the fonts up so that each plot is the saved the same way.
font = theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),  
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25), 
        legend.title=element_text(size=25), legend.text=element_text(size=25))
```

# Peak features
## Peak counts, intensity and length. 

```{r}
unfilteredPeakFeatures <- function(fileList, combined.tbl.stack, peak.length.plot, peak.intensity.plot){
    files =list.files(fileList, pattern= ".narrowPeak", full.names=T) # create list of files in directory
    files = as.list(files)
    data = lapply(files, function(x) fread(x, header=FALSE, sep="\t", quote = "", na.strings=c("", "NA")))
    names(data) = c("enhancers","promoters","H3K27ac_only","H3K27ac","H3K4me3_H3K27ac", "H3K4me3_only","H3K4me3")
    df1 = Map(mutate, data, group = names(data))
    df1$H3K27ac_only$cre = "enhancers"
    df1$H3K4me3_only$cre = "promoters"
    df1$H3K4me3_H3K27ac$cre = "promoters"

    fullPeaks = rbind(df1$enhancers, df1$promoters, df1$H3K27ac, df1$H3K4me3)
    combinedPeaks = rbind(df1$H3K27ac_only, df1$H3K4me3_H3K27ac, df1$H3K4me3_only)
        
    ## Plot stacked bar graph with number of peaks for each histone mark
    combined.tbl <- with(combinedPeaks, table(group, cre))
    combined.tbl <- as.data.frame(combined.tbl)
    p = ggplot(combined.tbl, aes(factor(cre), Freq, fill=group)) + 
      geom_bar(position=position_stack(reverse = TRUE), stat="identity") +
      scale_fill_manual(values = c("#FF9D40",  "#37B6CE", "#04859D"))  + 
      theme_minimal() + ylab("Number of peaks") +
      xlab("")
    p
    pdf(file=paste0(plot_dir, combined.tbl.stack), width = 10, height = 7)
    print(p)
    dev.off()

    # Peak lengths for H3K4me3 and H3K27ac
    fullPeaks$length <- (fullPeaks$V3 - fullPeaks$V2)
    level_order <- c('promoter', 'enhancer', 'H3K4me3', 'H3K27ac')

    ## Plot peak lengths
    p = ggplot(peaks, aes(factor(group), y = log10(length)))+ geom_violin(aes(fill=factor(group), color=factor(group))) + geom_boxplot(aes(color=factor(group)), width = .15, 
    outlier.shape = NA,
    position = position_dodge(width=.1)
    ) + theme_bw() + xlab("") + ylab("Log10 Peak Length") 

    p <- ggplot(fullPeaks, aes(factor(group, level = level_order), y = log10(length))) + 
    geom_half_violin(aes(fill=factor(group), color=factor(group)),
    side = "r", 
    position = "dodge"
    )+
    geom_boxplot(aes(color=factor(group)),
    width = .15, 
    outlier.shape = NA,
    fill=c("#FCF8EC","#FCF8EC","#F5F6F7","#E4F3F1"),
    position = position_dodge(width=.1)
    ) +
    coord_cartesian(xlim = c(1.2, NA), clip = "off") + theme_bw() + xlab("") + ylab("Log10 Peak Length") 
    pdf(file=paste0(plot_dir, peak.length.plot), width = 10, height = 7)
    print(p +  scale_color_manual(values = c("#E9C46A","#E9C46A","#264653","#2A9D8F")) +
    scale_fill_manual(values = c("#F1DAA2","#F1DAA2","#AEBABF","#7AC2B9")) + coord_flip())
    dev.off()

    ## Plot peak intensity
    p <- ggplot(fullPeaks, aes(factor(group, level = level_order), y = log10(V7))) + 
    geom_half_violin(aes(fill=factor(group), color=factor(group)),
    side = "r", 
    position = "dodge"
    )+
    geom_boxplot(aes(color=factor(group)),
    width = .15, 
    outlier.shape = NA,
    fill=c("#FCF8EC","#FCF8EC","#F5F6F7","#E4F3F1"),
    position = position_dodge(width=.1)
    ) +
    coord_cartesian(xlim = c(1.2, NA), clip = "off") + theme_bw() + xlab("") + ylab("Log10 Peak Intensity") 
    pdf(file=paste0(plot_dir, peak.intensity.plot), width = 10, height = 7)
    print(p +  scale_color_manual(values = c("#E9C46A","#E9C46A","#264653","#2A9D8F")) +
    scale_fill_manual(values = c("#F1DAA2","#F1DAA2","#AEBABF","#7AC2B9")) + coord_flip())
    dev.off()  
}

unfilteredPeakFeatures(fileList = fullPeak_dir, combined.tbl.stack= "dunnart_combined_stacked.pdf",
peak.length.plot = "dunnart_fullPeaks_length.pdf", peak.intensity.plot = "dunnart_fullPeaks_intensity.pdf")

```
## Distance to the nearest TSS
Now see where the peaks are located in relation to the TSS. Promoters should be reasonably close to the TSS and enhancers more distal to the TSS. 
Plot distance to TSS for all unfiltered peaks 

```{r}
distanceToTSS <- function(fileList, enhancerTSSplot, promoterTSSplot, TSSplot){
    files =list.files(fileList, pattern= "annotation.txt", full.names=T) # create list of files in directory
    files = as.list(files)
    data = lapply(files, function(x) fread(x, header=TRUE, sep="\t", quote = "", na.strings=c("", "NA"))) # read in all files
    names(data) = c("enhancers","promoters","H3K27ac","H3K4me3")
    df1 = Map(mutate, data, mark = names(data))
    enhProm = list(df1$promoters, df1$enhancers)
    enhProm = suppressWarnings(lapply(enhProm, function(x) x[,log10_abs_dist:=log10(abs(distanceToTSS)+1)][,log10_abs_dist:=ifelse(distanceToTSS<0,-log10_abs_dist,log10_abs_dist)]))
    names(enhProm) = c("promoters","enhancers")

    pdf(file = paste0(plot_dir, enhancerTSSplot), width=10, height = 7)
    print(ggplot(enhProm$enhancers, aes(x=log10_abs_dist)) + 
    geom_density(alpha=0.5, color="#2A9D8F", fill="#2A9D8F") + 
    scale_y_continuous(limits=c(0,0.3), labels = scales::percent) + 
    scale_x_continuous(limits=c(-7, 7)) + theme_bw())
    dev.off()

    pdf(file = paste0(plot_dir, promoterTSSplot), width=10, height = 7)
    print(ggplot(enhProm$promoters, aes(x=log10_abs_dist)) + 
    geom_density(alpha=0.5, color="#2A9D8F", fill="#2A9D8F") + 
    scale_y_continuous(limits=c(0,0.3), labels = scales::percent) + 
    scale_x_continuous(limits=c(-7, 7)) + theme_bw())
    dev.off()

    enhProm = rbindlist(enhProm,)
    pdf(file = paste0(plot_dir, TSSplot), width=10, height = 7)
    print(ggplot(enhProm, aes(x=log10_abs_dist, fill=factor(mark), color=factor(mark))) + 
    geom_density(alpha=0.5) +scale_color_manual(values=c("#E9C46A", "#2A9D8F")) + scale_fill_manual(values=c("#E9C46A", "#2A9D8F")) + 
    scale_x_continuous(limits=c(-7, 7)) + theme_bw() + font)
    dev.off()

}
distanceToTSS(fileList = annot_dir, enhancerTSSplot="dunnart_enhancerTSS.pdf", 
promoterTSSplot="dunnart_promoterTSS.pdf", TSSplot = "dunnart_TSS.pdf")
```

From this we can see that the promoter peaks have a large amount of peaks a long way from the TSS - suggests that these are either actually enhancers or they represent unannotated transcripts. Probably a mixture of both based on comparison with mouse peaks (where the annotation is better) there are not as many peaks in this distal regions. Use k-means clustering to group the peaks to decide on a cut off for "promoter" peaks. This will be more conservative for what we identify as promoters.

## k-means clustering 

```{r}
kmeansCluster <- function(file, plot1, plot2, output){
  data = fread(file, header=TRUE, sep="\t", quote = "") # read in all files
  data = data[,log10_dist:=log10(abs(distanceToTSS)+1.1)][,log10_dist:=ifelse(distanceToTSS<0,-log10_dist,log10_dist)]
  data = data[,abs_dist:=log10(abs(distanceToTSS)+1.1)]

  data = data %>% dplyr::select("V4", "width", "V7", "distanceToTSS", "log10_dist", "abs_dist", "annotation")
  
  ## plot the number of peaks in each cluster
  ## Using the MacQueen algorithm instead of the default Lloyd 
  ## The algorithm is more efficient as it updates centroids more often and usually needs to
  ## perform one complete pass through the cases to converge on a solution.
  df = data[,5]
  cre.kmeans = kmeans(df, 3, iter.max=100, nstart=25, algorithm="MacQueen")  
  cre.kmeans_table = data.frame(cre.kmeans$size, cre.kmeans$centers)
  cre.kmeans_df = data.frame(Cluster = cre.kmeans$cluster, data)

  pdf(plot1, width=10, height = 7)
  p <- ggplot(data = cre.kmeans_df, aes(y = Cluster, fill=as.factor(Cluster), color=as.factor(Cluster))) +
  geom_bar()  +
  theme(plot.title = element_text(hjust = 0.5)) + theme_bw() + font
  pdf(plot1)
  print(p + scale_color_manual(values = c('#9EBCDA','#8C6BB1', "#4D004B")) + scale_fill_manual(values = c('#9EBCDA','#8C6BB1', "#4D004B")))
  dev.off()


  p <- ggplot(cre.kmeans_df, aes(x=log10_dist, fill=as.factor(Cluster), color=as.factor(Cluster))) + 
            geom_histogram(binwidth=0.1, position = 'identity')  +
            theme_bw()+ font
  pdf(plot2, width = 10, height = 7)
  print(p + scale_color_manual(values = c('#9EBCDA','#8C6BB1', "#4D004B")) + scale_fill_manual(values = c('#9EBCDA','#8C6BB1', "#4D004B")))
  dev.off()  

  write.table(cre.kmeans_df, output, sep="\t", quote=F, row.names=F)
  return(cre.kmeans_df)
}

promoter_kmeans = kmeansCluster(file = paste0(annot_dir, "dunnart_promoter_annotation.txt"),  plot1 = paste0(plot_dir, "promoter_kmeans_bar.pdf"), plot2 = paste0(plot_dir, "promoter_kmeans_histogram.pdf"), output = paste0(annot_dir, "promoter_kmeans_peaks.txt"))
```

Filter for cluster 1 and make final promoter/enhancer plots
```{r}
plotPeakClusters <- function(x, y, enhancer, promoter, plotTSS, peakIntensityPlot, peakWidthPlot, annotation){
  enhancer.annot= fread(enhancer, header=TRUE, sep="\t", quote = "") 
  enhancer.annot = enhancer.annot[,log10_dist:=log10(abs(distanceToTSS)+1)][,log10_dist:=ifelse(distanceToTSS<0,-log10_dist,log10_dist)]
  enhancer.annot = enhancer.annot[,abs_dist:=abs(distanceToTSS)]
  promoter.annot = fread(promoter, header=TRUE, sep="\t", quote = "")
  promoter.annot = promoter.annot[,log10_dist:=log10(abs(distanceToTSS)+1)][,log10_dist:=ifelse(distanceToTSS<0,-log10_dist,log10_dist)]
  promoter.annot = promoter.annot[,abs_dist:=abs(distanceToTSS)]

  promoter.annot$label = "promoter"
  enhancer.annot$label = "enhancer"
  enhancer.annot = enhancer.annot %>% dplyr::select("V4", "width", "V7", "distanceToTSS", "log10_dist", "abs_dist", "annotation", "label")
  promoter.annot = promoter.annot %>% dplyr::select("V4", "width", "V7", "distanceToTSS", "log10_dist", "abs_dist", "annotation", "label")

  promoter.kmeans = fread(x, header=TRUE, sep="\t", quote = "") 
  promoter.kmeans$cre = "promoter"

  for (i in 1:nrow(promoter.kmeans)) {
    if(promoter.kmeans$Cluster[i]=='1' & promoter.kmeans$cre[i]=='promoter') {
            promoter.kmeans[i, 'label'] <- "promoter cluster 1"
            }
            else if(promoter.kmeans$Cluster[i]=='2' & promoter.kmeans$cre[i]=='promoter') {
              promoter.kmeans[i, 'label'] <- "promoter cluster 2"
              }
              else if(promoter.kmeans$Cluster[i]=='3' & promoter.kmeans$cre[i]=='promoter') {
                promoter.kmeans[i, 'label'] <- "promoter cluster 3"
                }
  }

  data2 = promoter.kmeans %>% dplyr::select("V4", "width", "V7", "distanceToTSS", "log10_dist", "abs_dist", "annotation", "label")
  all_peaks = rbind(data2, enhancer.annot, promoter.annot)
  all_peaks = as.data.table(all_peaks)
  all_peaks = all_peaks[,log10_intensity:=log10(V7)]
  all_peaks = all_peaks[,log10_width:=log10(width)]

  colors = c("#E9C46A","#e34a33", "#fdbb84","#fee8c8", "#2A9D8F")
 
  ## Plot distance to TSS
  pdf(plotTSS, width=10, height = 7)
  print(ggplot(all_peaks, aes(x=log10_dist, colour = factor(Cluster), fill=factor(Cluster))) + geom_density(aes(x = log10_dist, y = ..density..), position="stack", alpha=0.7) + 
  theme_bw() + scale_fill_manual(values = colors)+ 
  scale_color_manual(values = colors) + font)
  dev.off()

  my_comparisons = list( c("promoter cluster 1", "promoter cluster 2"), c("promoter cluster 1", "promoter cluster 3"), c("promoter cluster 1", "promoter"), c("promoter cluster 1", "enhancer") )
  ## Plot peak intensity
  p <- ggplot(all_peaks, aes(factor(label), y = log10_intensity)) + 
  geom_violin(aes(fill=factor(label), color=factor(label)),
   position = "dodge"
   )+
  geom_boxplot(aes(color=factor(label)),
    outlier.shape = NA,
    width = .15, 
    notch = TRUE,
    position = position_dodge(width=.1)
  ) + theme_bw() + xlab("") + ylab("Log 10 peak intensity") 
  pdf("test.pdf", width=10, height = 8)
  print(p + scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) + font + stat_compare_means(comparisons = my_comparisons)) 
  dev.off()

  ## Plot peak width
  p <- ggplot(all_peaks, aes(factor(label), y = log10_width)) + 
  geom_violin(aes(fill=factor(label), color=factor(label)),
   position = "dodge"
   )+
  geom_boxplot(aes(color=factor(label)),
    outlier.shape = NA,
    width = .15, 
    notch = TRUE,
    position = position_dodge(width=.1)
  ) + theme_bw() + xlab("") + ylab("Log 10 peak width") 
  pdf(peakWidthPlot, width=9, height = 8)
  print(p + scale_color_manual(values =colors) +
  scale_fill_manual(values = colors) + font + stat_compare_means(comparisons = my_comparisons))
  dev.off()

  ## Plot genomic regions
  df2 = rbind(promoter_kmeans)
    #df1 = rbindlist(df1,) ## bind rows back together
  df2 = map_df(df2, ~ gsub(" ().*", "", .x))# remove everything after the first space
  #promoters_only = df2[complete.cases(df2), ]
  tbl = with(df2, table(annotation, Cluster)) %>% as.data.frame()
  pdf(annotation)
    ggplot(tbl, aes(factor(annotation), Freq, fill=factor(Cluster))) + 
    geom_bar(position=position_stack(reverse = TRUE), stat="identity") +
    #geom_text(data=subset(data,Freq != 0),aes(label=Freq, y=pos), size=3)+
    scale_fill_manual(values = c('#9EBCDA','#8C6BB1', "#4D004B"))  + 
    theme_minimal() + ylab("Number of peaks") +
    xlab("")
    dev.off()
}
plotPeakClusters(peakWidthPlot = paste0(plot_dir, "peakWidthPlot.pdf"),plotTSS =paste0(plot_dir,  "peakDistanceToTSS.pdf"),
peakIntensityPlot = paste0(plot_dir, "peakIntensityPlot.pdf"), annotation = paste0(plot_dir, "peakAnnotation.pdf"),
x= paste0(annot_dir, "promoter_kmeans_peaks.txt"), enhancer = paste0(annot_dir, "dunnart_enhancer_annotation.txt"), 
promoter = paste0(annot_dir, "dunnart_promoter_annotation.txt"))

## Extract cluster groups from narrowPeak files and save separately
cluster1 <- promoter.kmeans$V4[promoter.kmeans$Cluster==1]
cluster2 <- promoter.kmeans$V4[promoter.kmeans$Cluster==2]
cluster3 <- promoter.kmeans$V4[promoter.kmeans$Cluster==3]

cluster1 <- enhancer_kmeans$V4[enhancer_kmeans$Cluster==1]
cluster2 <- enhancer_kmeans$V4[enhancer_kmeans$Cluster==2]
cluster3 <- enhancer_kmeans$V4[enhancer_kmeans$Cluster==3]


extractClusters = function(promoter, cluster1, cluster2, cluster3, out1, out2, out3){
  file= fread(promoter, header=FALSE, sep="\t", quote = "") 
  write.table(subset(file, V4 %in% cluster1), out1, quote=FALSE, col.names=FALSE, row.names=FALSE, sep="\t")
  write.table(subset(file, V4 %in% cluster2), out2, quote=FALSE, col.names=FALSE, row.names=FALSE, sep="\t")
  write.table(subset(file, V4 %in% cluster3), out3, quote=FALSE, col.names=FALSE, row.names=FALSE, sep="\t")
}

extractClusters(promoter = "dunnart_promoters.narrowPeak", out1 = "cluster1_promoters.narrowPeak", 
out2 ="cluster2_promoters.narrowPeak" , out3 = "cluster3_promoters.narrowPeak", cluster1 = cluster1, 
cluster2 = cluster2, cluster3 = cluster3)

extractClusters(promoter = "dunnart_enhancers.narrowPeak", out1 = "cluster1_enhancers.narrowPeak", 
out2 ="cluster2_enhancers.narrowPeak" , out3 = "cluster3_enhancers.narrowPeak", cluster1 = cluster1, 
cluster2 = cluster2, cluster3 = cluster3)

```

```{r}
distanceToTSS <- function(fileList, enhancerTSSplot, promoterTSSplot, TSSplot){
    files =list.files(fileList, pattern= "annotation.txt", full.names=T) # create list of files in directory
    files = as.list(files)
    data = lapply(files, function(x) fread(x, header=TRUE, sep="\t", quote = "", na.strings=c("", "NA"))) # read in all files
    names(data) = c("cluster1", "cluster2", "cluster3", "enhancers","promoters","H3K27ac","H3K4me3")
    enhProm = Map(mutate, data, mark = names(data))
    #promoter_5kb = x
    #promoter_5kb$mark = "promoter_5kb"
    #enhProm = list(df1$enhancers, df1$promoters)
    enhProm = suppressWarnings(lapply(enhProm, function(x) x[,log10_abs_dist:=log10(abs(distanceToTSS)+1)][,log10_abs_dist:=ifelse(distanceToTSS<0,-log10_abs_dist,log10_abs_dist)]))
    enhProm = suppressWarnings(lapply(enhProm, function(x) x[,abs_dist:=abs(distanceToTSS)]))
    #names(enhProm) = c("enhancers","promoters", "promoter_5kb")
    level_order = c("cluster1", "cluster2", "cluster3", "promoters", "enhancers", "H3K4me3", "H3K27ac")

    pdf(file = paste0(plot_dir, enhancerTSSplot), width=10, height = 7)
    print(ggplot(enhProm$enhancers, aes(x=log10_abs_dist, color=factor(mark), fill=factor(mark))) + 
    geom_density(alpha=0.5) + theme_bw() + scale_color_manual(values = c('#E9C46A')) 
    + scale_fill_manual(values = c('#E9C46A')) + font) 
    dev.off()

    enhProm = rbind(enhProm$promoters, enhProm$cluster1, enhProm$cluster2, enhProm$cluster3 ,use.names=TRUE)
    pdf(file = paste0(plot_dir, TSSplot), width=15, height = 7)
    print(ggplot(enhProm, aes(x=log10_abs_dist, color = factor(mark, level=level_order), fill = factor(mark, level=level_order))) + 
    geom_density(position = "stack", alpha=0.8) + 
    theme_bw() )
    #+ scale_color_manual(values = c('#4D004B', '#E9C46A','#2A9D8F')) 
    #+ scale_fill_manual(values = c('#4D004B', '#E9C46A','#2A9D8F')) + font) 
    dev.off()
}
distanceToTSS(fileList = annot_dir, enhancerTSSplot="dunnart_enhancerTSS.pdf", promoterTSSplot="dunnart_promoterTSS.pdf",
TSSplot = "dunnart_TSS.pdf")
```

## Now look at CpG% and GC% for these groups
Run Homer on the clusters 

```{r}
GCcontent = function(fileList, gcPlot, cpgPlot, dataframestobind){
    files =list.files(fileList, pattern= "homerAnnot.txt", full.names=T) # create list of files in directory
    files = as.list(files)
    data = lapply(files, function(x) fread(x, header=TRUE, sep="\t", quote = "", na.strings=c("", "NA"))) # read in all files
    names(data) = c("cluster1","cluster2","cluster3","enhancers", "promoters")
    df1 = Map(mutate, data, group = names(data))
    df1 = lapply(df1, function(x) x %>% dplyr::select("Chr", "Start", "End", "Peak Score", "Distance to TSS", "CpG%", "GC%", "group") %>% as.data.table())
    df1 = rbind(df1$cluster1, df1$cluster2, df1$cluster3, df1$promoters, df1$enhancers)
    colnames(df1)[5:7] <- c("distanceToTSS","CpG", "GC")
    df1[is.na(df1)] <- 0
    df1 = df1[,log10_abs_dist:=log10(abs(distanceToTSS)+1)][,log10_abs_dist:=ifelse(distanceToTSS<0,-log10_abs_dist,log10_abs_dist)]

    my_comparisons = list( c("cluster1", "cluster2"), c("cluster1", "cluster3"), c("cluster1", "promoters"), 
    c("cluster1", "enhancers"), c("promoters", "enhancers"), c("promoters", "cluster2"), 
    c("promoters", "cluster3"), c("enhancers", "cluster2"), c("enhancers", "cluster3"), c("cluster2", "cluster3") )

  p <- ggplot(df1, aes(factor(group), y = GC)) + 
    geom_violin(aes(fill=factor(group), color=factor(group)),
    position = "dodge"
    )+
  geom_boxplot(aes(color=factor(group)),
    outlier.shape = NA,
    width = .15, 
    notch = TRUE,
    fill=c("#E7EEF6","#D4C7E2","#D3BFD2", "#FCF8EC","#E4F3F1"),
    position = position_dodge(width=.1)
  ) + theme_bw() + xlab("") + ylab("GC content") 
  pdf(gcPlot, width=9, height = 8)
  print(p + font + scale_color_manual(values = c('#9EBCDA','#8C6BB1','#4D004B', '#E9C46A','#2A9D8F')) +
  scale_fill_manual(values = c("#B6CDE3","#A990C4","#7A4078" ,"#F1DAA2","#7AC2B9")) + stat_compare_means(p.adjust.method = "fdr", comparisons = my_comparisons))
  dev.off()

  p <- ggplot(df1, aes(factor(group), y = CpG)) + 
  geom_violin(aes(fill=factor(group), color=factor(group)),
   position = "dodge"
   )+
  geom_boxplot(aes(color=factor(group)),
    outlier.shape = NA,
    width = .15, 
    notch = TRUE,
    fill=c("#E7EEF6","#D4C7E2","#D3BFD2", "#FCF8EC","#E4F3F1"),
    position = position_dodge(width=.1)
  ) + theme_bw() + xlab("") + ylab("CpG") 
  pdf(cpgPlot, width=9, height = 8)
  print(p + font + scale_color_manual(values = c('#9EBCDA','#8C6BB1','#4D004B', '#E9C46A','#2A9D8F')) +
  scale_fill_manual(values = c("#B6CDE3","#A990C4","#7A4078" ,"#F1DAA2","#7AC2B9")) + stat_compare_means(p.adjust.method = "fdr", comparisons = my_comparisons))
  dev.off()
}
GCcontent(fileList = annot_dir, gcPlot = paste0(plot_dir, "dunnart_GC.pdf"), cpgPlot = paste0(plot_dir, "dunnart_cpg.pdf"))

```



# Annotate dunnart peaks
The easiest way to call the nearest genes for the peaks in the dunnart is to use the ChIPseeker package (Guangchuang Yu 2021) as it allows easy integration of non-model organism genomes and has well documented instructions on incorporating BYO genomes with the package.
To use the ChIPseeker to annotate peaks, firstly a txdb is needed for the dunnart annotation file. A TxDb class is a container for storing transcript annotations. The dunnart genome doesn't have a de novo annotation so instead the Tasmanian devil annotation (RefSeq) has been lifted over to the dunnart genome using LiftOff (https://github.com/agshumate/Liftoff). 

```{r}
## Make txdb for dunnart annotation file
setwd("/data/projects/punim0586/lecook/chipseq-cross-species/data/genomic_data")
smiCra_txdb <- makeTxDbFromGFF("Scras_dunnart_assem1.0_pb-ont-illsr_flyeassem_red-rd-scfitr2_pil2xwgs2_60chr2.gff")
```

For downstream analyses, conversion tables between gene databases and between species is needed.
This is because the ENSEMBL/ENTREZ IDs for the Tasmanian Devil have fewer links to databases such as GO terms etc.
For this I have two conversion tables: 
1. Converts Tasmanian devil RefSeq to Tasmanian Devil ENSEMBL IDs
2. Convert Tasmanian Devil ENSEMBL IDs to mouse ENSEMBL IDs

```{r}
## geneID conversion tables
setwd("/data/projects/punim0586/lecook/chipseq-pipeline/cross_species/peakAnnotation/")
df2 <- read.table("devil_to_mouse_ensembl.txt", header=TRUE, sep="\t") ## conversion table for devil ENSEMBL to mouse ENSEMBL
df3 <- read.table("refseq_to_ensembl.txt", header=TRUE, sep="\t") ## convertsion table for devil refseq to devil ENSEMBL
```