---
title: "Cross-species peak level comparisons"
author: "lecook"
date: "2022-02-23"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(knitr)

plot_dir <- "output/plots/"
fullPeak_dir <- "output/peaks/"
annot_dir <- "output/annotations/"
filterPeaks_dir <- "output/filtered_peaks/"
liftover_dir <- "output/liftover/"
```

# Summary tables
After the tables is all the code to compare peaks between species using liftOver and bedtools. It is a lot of repetitive code that I could revise but it was easiest to track it all this way for now. The summary tables show the number of peaks for the different overlaps.

## Number of peaks lifted over with no width filtering
```{r echo=FALSE}
files <- list.files(liftover_dir, pattern = "dunnart_enhancer_smiCraTOmm10.bed|dunnart_promoter_smiCraTOmm10.bed", full.names = T)
files <- as.list(files)
data <- lapply(files, function(x) data.table::fread(x, header = FALSE, sep = "\t", quote = "", na.strings = c("", "NA")))

df <- data.table(enhancer_peaks_smiCraTOmm10 = dim(data[[1]])[1], promoter_peak_smiCraTOmm10 = dim(data[[2]])[1])

kable(df, caption="Table. Number of peaks lifted over from dunnart to mouse")
```

```{r}


```



# LiftOver of peak coordinates between species
## All peaks with no peak width filtering

```{bash eval=FALSE}
## Load modules
conda activate chip
module load ucsc

## Extract peak coordinates
less output/peaks/dunnart_enhancer_peaks.narrowPeak | awk '{print $1,$2,$3}' > output/peaks/dunnart_enhancer_peaks_coord.bed
less output/filtered_peaks/cluster1_dunnart_promoter_peaks.narrowPeak | awk '{print $1,$2,$3}' > output/filtered_peaks/dunnart_promoter_peaks_coord.bed

## LiftOver peak coordinates from dunnart to mouse
liftOver output/peaks/dunnart_enhancer_peaks_coord.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_smiCraTOmm10.bed output/liftover/dunnart_enhancer_smiCraTOmm10_unmapped.bed
liftOver output/filtered_peaks/dunnart_promoter_peaks_coord.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_smiCraTOmm10.bed output/liftover/dunnart_promoter_smiCraTOmm10_unmapped.bed
```

<!-- # Import output files in R -->
<!-- enh = fread("enhancers/dunnart.enhancer_smiCraTOmm10.bed") -->
<!-- prom = fread("promoters/clustered/dunnart.promoter_smiCraTOmm10.bed") -->
<!-- data = list(enh, prom) -->
<!-- names(data) = c("enhancers", "promoters") -->
<!-- data = Map(mutate, data, cre = names(data)) -->
<!-- data = lapply(data, function(x) x[order(V4),]) -->
<!-- data = lapply(data, function(x) x=x[,width:=V3-V2]) -->
<!-- data = rbindlist(data,) -->

## LiftOver peak summits
### Prepare peak summits and extract peak IDs
```{bash eval=FALSE}

## Extract peak IDs
less output/peaks/dunnart_enhancer_peaks.narrowPeak | awk -F '\t' '{print $4}' | sort > output/peaks/dunnart_enhancer_peaks_IDs.txt
less output/filtered_peaks/cluster1_dunnart_promoter_peaks.narrowPeak | awk -F '\t' '{print $4}' | sort > output/filtered_peaks/dunnart_promoter_peaks_IDs.txt

less output/peaks/E10.5_enhancer_peaks.narrowPeak | awk -F '\t' '{print $4}'  >  output/peaks/E10.5_enhancer_peaks_IDs.txt
less  output/peaks/E11.5_enhancer_peaks.narrowPeak | awk -F '\t' '{print $4}'  >  output/peaks/E11.5_enhancer_peaks_IDs.txt
less  output/peaks/E12.5_enhancer_peaks.narrowPeak | awk -F '\t' '{print $4}'  >  output/peaks/E12.5_enhancer_peaks_IDs.txt
less  output/peaks/E13.5_enhancer_peaks.narrowPeak | awk -F '\t' '{print $4}'  >  output/peaks/E13.5_enhancer_peaks_IDs.txt
less  output/peaks/E14.5_enhancer_peaks.narrowPeak | awk -F '\t' '{print $4}'  >  output/peaks/E14.5_enhancer_peaks_IDs.txt
less  output/peaks/E15.5_enhancer_peaks.narrowPeak | awk -F '\t' '{print $4}'  >  output/peaks/E15.5_enhancer_peaks_IDs.txt

less  output/filtered_peaks/E10_cluster1_peaks.narrowPeak | awk -F '\t' '{print $4}' > output/filtered_peaks/E10.5_promoter_peaks_IDs.txt
less  output/filtered_peaks/E11_cluster1_peaks.narrowPeak | awk -F '\t' '{print $4}'  > output/filtered_peaks/E11.5_promoter_peaks_IDs.txt
less  output/filtered_peaks/E12_cluster1_peaks.narrowPeak | awk -F '\t' '{print $4}'  > output/filtered_peaks/E12.5_promoter_peaks_IDs.txt
less  output/filtered_peaks/E13_cluster1_peaks.narrowPeak | awk -F '\t' '{print $4}'  > output/filtered_peaks/E13.5_promoter_peaks_IDs.txt
less  output/filtered_peaks/E14_cluster1_peaks.narrowPeak | awk -F '\t' '{print $4}'  > output/filtered_peaks/E14.5_promoter_peaks_IDs.txt
less  output/filtered_peaks/E15_cluster1_peaks.narrowPeak | awk -F '\t' '{print $4}'  > output/filtered_peaks/E15.5_promoter_peaks_IDs.txt

## Concatenate pooled summit peak files 

cat output/peaks/H3K4me3_pooled_macs2_default_summits.bed output/peaks/H3K27ac_pooled_macs2_default_summits.bed > output/peaks/H3K4me3_H3K27ac_dunnart_pooled_default_combinedSummits.bed

cat output/peaks/E10.5_H3K27ac.pooled.macs2_summits.bed output/peaks/E10.5_H3K4me3.pooled.macs2_summits.bed > output/peaks/E10.5_H3K27ac_H3K4me3.pooled.macs2_combinedSummits.bed
cat output/peaks/E11.5_H3K27ac.pooled.macs2_summits.bed output/peaks/E11.5_H3K4me3.pooled.macs2_summits.bed > output/peaks/E11.5_H3K27ac_H3K4me3.pooled.macs2_combinedSummits.bed
cat output/peaks/E12.5_H3K27ac.pooled.macs2_summits.bed output/peaks/E12.5_H3K4me3.pooled.macs2_summits.bed > output/peaks/E12.5_H3K27ac_H3K4me3.pooled.macs2_combinedSummits.bed
cat output/peaks/E13.5_H3K27ac.pooled.macs2_summits.bed output/peaks/E13.5_H3K4me3.pooled.macs2_summits.bed > output/peaks/E13.5_H3K27ac_H3K4me3.pooled.macs2_combinedSummits.bed
cat output/peaks/E14.5_H3K27ac.pooled.macs2_summits.bed output/peaks/E14.5_H3K4me3.pooled.macs2_summits.bed > output/peaks/E14.5_H3K27ac_H3K4me3.pooled.macs2_combinedSummits.bed
cat output/peaks/E15.5_H3K27ac.pooled.macs2_summits.bed output/peaks/E15.5_H3K4me3.pooled.macs2_summits.bed > output/peaks/E15.5_H3K27ac_H3K4me3.pooled.macs2_combinedSummits.bed

```

### Extract rows from summits file based on enhancer and promoter peak IDs
```{r eval=FALSE}

files =list.files(fullPeak_dir, pattern= "macs2_combinedSummits.bed|default_combinedSummits.bed", full.names=T) # create list of files in directory
files = as.list(files)
summits = lapply(files, function(x) fread(x, header=FALSE, sep="\t", quote = "", na.strings=c("", "NA")))
names(summits) <- c("E10", "E11", "E12", "E13", "E14", "E15", "dunnart")

files2 =list.files(fullPeak_dir, pattern= "peaks_IDs.txt", full.names=T) # create list of files in directory
files3 = list.files(filterPeaks_dir, pattern = "peaks_IDs.txt", full.names=T)
files = append(files2, files3)
filenames <- sub('\\_peaks_IDs.txt$', '', basename(files)) 

files = as.list(files)

peak_IDs = lapply(files, function(x) fread(x, header=FALSE, sep="\t", quote = "", na.strings=c("", "NA")))
names(peak_IDs) <- filenames

filtered <- lapply(summits, function(x) x[x$V4 %in% unlist(as.vector(peak_IDs)),])
filtered <- lapply(filtered, function(x) substr(x$V4, 1, 13))

filtered_bind <- rbindlist(filtered,)
filtered_bind$V4 <- substr(filtered_bind$V4, 1,13)
filtered_split <- split(filtered_bind, by = "V4")

names(filtered_split) <- c("E10.5_enhancer", "E10.5_promoter", 
                           "E11.5_enhancer", "E11.5_promoter",
                           "E12.5_enhancer", "E12.5_promoter",
                           "E13.5_enhancer", "E13.5_promoter",
                           "E14.5_enhancer", "E14.5_promoter",
                           "E15.5_enhancer", "E15.5_promoter",
                           "dunnart_promoter", "dunnart_enhancer")

lapply(names(filtered_split), function(x) write.table(filtered_split[[x]], file=paste0("output/liftover/",x,"_summits", ".bed"), sep="\t", quote=FALSE, col.names=FALSE, row.names=FALSE))
```

### Extend the summits 25bp in both directions

```{bash eval=FALSE}
bedtools slop -i output/liftover/dunnart_promoter_summits.bed -b 25 -g data/genomic_data/smiCra1.chrom.sizes > output/liftover/dunnart_promoter_50bpsummits.bed

bedtools slop -i output/liftover/dunnart_enhancer_summits.bed -b 25 -g data/genomic_data/smiCra1.chrom.sizes > output/liftover/dunnart_enhancer_50bpsummits.bed

bedtools slop -i output/liftover/E10.5_enhancer_summits.bed -b 25 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E10.5_enhancer_50bpsummits.bed
bedtools slop -i output/liftover/E11.5_enhancer_summits.bed -b 25 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E11.5_enhancer_50bpsummits.bed
bedtools slop -i output/liftover/E12.5_enhancer_summits.bed -b 25 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E12.5_enhancer_50bpsummits.bed
bedtools slop -i output/liftover/E13.5_enhancer_summits.bed -b 25 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E13.5_enhancer_50bpsummits.bed
bedtools slop -i output/liftover/E14.5_enhancer_summits.bed -b 25 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E14.5_enhancer_50bpsummits.bed
bedtools slop -i output/liftover/E15.5_enhancer_summits.bed -b 25 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E15.5_enhancer_50bpsummits.bed

bedtools slop -i output/liftover/E10.5_promoter_summits.bed -b 25 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E10.5_promoter_50bpsummits.bed
bedtools slop -i output/liftover/E11.5_promoter_summits.bed -b 25 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E11.5_promoter_50bpsummits.bed
bedtools slop -i output/liftover/E12.5_promoter_summits.bed -b 25 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E12.5_promoter_50bpsummits.bed
bedtools slop -i output/liftover/E13.5_promoter_summits.bed -b 25 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E13.5_promoter_50bpsummits.bed
bedtools slop -i output/liftover/E14.5_promoter_summits.bed -b 25 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E14.5_promoter_50bpsummits.bed
bedtools slop -i output/liftover/E15.5_promoter_summits.bed -b 25 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E15.5_promoter_50bpsummits.bed
```

### Extend the summits 50bp in both directions
```{bash eval=FALSE}
bedtools slop -i output/liftover/dunnart_promoter_summits.bed -b 50 -g data/genomic_data/smiCra1.chrom.sizes > output/liftover/dunnart_promoter_100bpsummits.bed

bedtools slop -i output/liftover/dunnart_enhancer_summits.bed -b 50 -g data/genomic_data/smiCra1.chrom.sizes > output/liftover/dunnart_enhancer_100bpsummits.bed

bedtools slop -i output/liftover/E10.5_enhancer_summits.bed -b 50 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E10.5_enhancer_100bpsummits.bed
bedtools slop -i output/liftover/E11.5_enhancer_summits.bed -b 50 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E11.5_enhancer_100bpsummits.bed
bedtools slop -i output/liftover/E12.5_enhancer_summits.bed -b 50 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E12.5_enhancer_100bpsummits.bed
bedtools slop -i output/liftover/E13.5_enhancer_summits.bed -b 50 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E13.5_enhancer_100bpsummits.bed
bedtools slop -i output/liftover/E14.5_enhancer_summits.bed -b 50 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E14.5_enhancer_100bpsummits.bed
bedtools slop -i output/liftover/E15.5_enhancer_summits.bed -b 50 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E15.5_enhancer_100bpsummits.bed

bedtools slop -i output/liftover/E10.5_promoter_summits.bed -b 50 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E10.5_promoter_100bpsummits.bed
bedtools slop -i output/liftover/E11.5_promoter_summits.bed -b 50 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E11.5_promoter_100bpsummits.bed
bedtools slop -i output/liftover/E12.5_promoter_summits.bed -b 50 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E12.5_promoter_100bpsummits.bed
bedtools slop -i output/liftover/E13.5_promoter_summits.bed -b 50 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E13.5_promoter_100bpsummits.bed
bedtools slop -i output/liftover/E14.5_promoter_summits.bed -b 50 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E14.5_promoter_100bpsummits.bed
bedtools slop -i output/liftover/E15.5_promoter_summits.bed -b 50 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E15.5_promoter_100bpsummits.bed
```

### Extend the summits 100bp in both directions
```{bash eval=FALSE}
bedtools slop -i output/liftover/dunnart_promoter_summits.bed -b 100 -g data/genomic_data/smiCra1.chrom.sizes > output/liftover/dunnart_promoter_200bpsummits.bed

bedtools slop -i output/liftover/dunnart_enhancer_summits.bed -b 100 -g data/genomic_data/smiCra1.chrom.sizes > output/liftover/dunnart_enhancer_200bpsummits.bed

bedtools slop -i output/liftover/E10.5_enhancer_summits.bed -b 100 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E10.5_enhancer_200bpsummits.bed
bedtools slop -i output/liftover/E11.5_enhancer_summits.bed -b 100 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E11.5_enhancer_200bpsummits.bed
bedtools slop -i output/liftover/E12.5_enhancer_summits.bed -b 100 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E12.5_enhancer_200bpsummits.bed
bedtools slop -i output/liftover/E13.5_enhancer_summits.bed -b 100 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E13.5_enhancer_200bpsummits.bed
bedtools slop -i output/liftover/E14.5_enhancer_summits.bed -b 100 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E14.5_enhancer_200bpsummits.bed
bedtools slop -i output/liftover/E15.5_enhancer_summits.bed -b 100 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E15.5_enhancer_200bpsummits.bed

bedtools slop -i output/liftover/E10.5_promoter_summits.bed -b 100 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E10.5_promoter_200bpsummits.bed
bedtools slop -i output/liftover/E11.5_promoter_summits.bed -b 100 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E11.5_promoter_200bpsummits.bed
bedtools slop -i output/liftover/E12.5_promoter_summits.bed -b 100 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E12.5_promoter_200bpsummits.bed
bedtools slop -i output/liftover/E13.5_promoter_summits.bed -b 100 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E13.5_promoter_200bpsummits.bed
bedtools slop -i output/liftover/E14.5_promoter_summits.bed -b 100 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E14.5_promoter_200bpsummits.bed
bedtools slop -i output/liftover/E15.5_promoter_summits.bed -b 100 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E15.5_promoter_200bpsummits.bed
```

### Extend the summits 150bp in both directions
```{bash eval=FALSE}
bedtools slop -i output/liftover/dunnart_promoter_summits.bed -b 150 -g data/genomic_data/smiCra1.chrom.sizes > output/liftover/dunnart_promoter_300bpsummits.bed

bedtools slop -i output/liftover/dunnart_enhancer_summits.bed -b 150 -g data/genomic_data/smiCra1.chrom.sizes > output/liftover/dunnart_enhancer_300bpsummits.bed

bedtools slop -i output/liftover/E10.5_enhancer_summits.bed -b 150 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E10.5_enhancer_300bpsummits.bed
bedtools slop -i output/liftover/E11.5_enhancer_summits.bed -b 150 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E11.5_enhancer_300bpsummits.bed
bedtools slop -i output/liftover/E12.5_enhancer_summits.bed -b 150 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E12.5_enhancer_300bpsummits.bed
bedtools slop -i output/liftover/E13.5_enhancer_summits.bed -b 150 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E13.5_enhancer_300bpsummits.bed
bedtools slop -i output/liftover/E14.5_enhancer_summits.bed -b 150 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E14.5_enhancer_300bpsummits.bed
bedtools slop -i output/liftover/E15.5_enhancer_summits.bed -b 150 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E15.5_enhancer_300bpsummits.bed

bedtools slop -i output/liftover/E10.5_promoter_summits.bed -b 150 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E10.5_promoter_300bpsummits.bed
bedtools slop -i output/liftover/E11.5_promoter_summits.bed -b 150 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E11.5_promoter_300bpsummits.bed
bedtools slop -i output/liftover/E12.5_promoter_summits.bed -b 150 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E12.5_promoter_300bpsummits.bed
bedtools slop -i output/liftover/E13.5_promoter_summits.bed -b 150 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E13.5_promoter_300bpsummits.bed
bedtools slop -i output/liftover/E14.5_promoter_summits.bed -b 150 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E14.5_promoter_300bpsummits.bed
bedtools slop -i output/liftover/E15.5_promoter_summits.bed -b 150 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E15.5_promoter_300bpsummits.bed
```

### Extend the summits 200bp in both directions
```{bash eval=FALSE}
bedtools slop -i output/liftover/dunnart_promoter_summits.bed -b 200 -g data/genomic_data/smiCra1.chrom.sizes > output/liftover/dunnart_promoter_400bpsummits.bed

bedtools slop -i output/liftover/dunnart_enhancer_summits.bed -b 200 -g data/genomic_data/smiCra1.chrom.sizes > output/liftover/dunnart_enhancer_400bpsummits.bed

bedtools slop -i output/liftover/E10.5_enhancer_summits.bed -b 200 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E10.5_enhancer_400bpsummits.bed
bedtools slop -i output/liftover/E11.5_enhancer_summits.bed -b 200 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E11.5_enhancer_400bpsummits.bed
bedtools slop -i output/liftover/E12.5_enhancer_summits.bed -b 200 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E12.5_enhancer_400bpsummits.bed
bedtools slop -i output/liftover/E13.5_enhancer_summits.bed -b 200 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E13.5_enhancer_400bpsummits.bed
bedtools slop -i output/liftover/E14.5_enhancer_summits.bed -b 200 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E14.5_enhancer_400bpsummits.bed
bedtools slop -i output/liftover/E15.5_enhancer_summits.bed -b 200 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E15.5_enhancer_400bpsummits.bed

bedtools slop -i output/liftover/E10.5_promoter_summits.bed -b 200 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E10.5_promoter_400bpsummits.bed
bedtools slop -i output/liftover/E11.5_promoter_summits.bed -b 200 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E11.5_promoter_400bpsummits.bed
bedtools slop -i output/liftover/E12.5_promoter_summits.bed -b 200 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E12.5_promoter_400bpsummits.bed
bedtools slop -i output/liftover/E13.5_promoter_summits.bed -b 200 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E13.5_promoter_400bpsummits.bed
bedtools slop -i output/liftover/E14.5_promoter_summits.bed -b 200 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E14.5_promoter_400bpsummits.bed
bedtools slop -i output/liftover/E15.5_promoter_summits.bed -b 200 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E15.5_promoter_400bpsummits.bed
```

### Extend the summits 250bp in both directions
```{bash eval=FALSE}
bedtools slop -i output/liftover/dunnart_promoter_summits.bed -b 250 -g data/genomic_data/smiCra1.chrom.sizes > output/liftover/dunnart_promoter_500bpsummits.bed

bedtools slop -i output/liftover/dunnart_enhancer_summits.bed -b 250 -g data/genomic_data/smiCra1.chrom.sizes > output/liftover/dunnart_enhancer_500bpsummits.bed

bedtools slop -i output/liftover/E10.5_enhancer_summits.bed -b 250 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E10.5_enhancer_500bpsummits.bed
bedtools slop -i output/liftover/E11.5_enhancer_summits.bed -b 250 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E11.5_enhancer_500bpsummits.bed
bedtools slop -i output/liftover/E12.5_enhancer_summits.bed -b 250 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E12.5_enhancer_500bpsummits.bed
bedtools slop -i output/liftover/E13.5_enhancer_summits.bed -b 250 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E13.5_enhancer_500bpsummits.bed
bedtools slop -i output/liftover/E14.5_enhancer_summits.bed -b 250 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E14.5_enhancer_500bpsummits.bed
bedtools slop -i output/liftover/E15.5_enhancer_summits.bed -b 250 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E15.5_enhancer_500bpsummits.bed

bedtools slop -i output/liftover/E10.5_promoter_summits.bed -b 250 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E10.5_promoter_500bpsummits.bed
bedtools slop -i output/liftover/E11.5_promoter_summits.bed -b 250 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E11.5_promoter_500bpsummits.bed
bedtools slop -i output/liftover/E12.5_promoter_summits.bed -b 250 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E12.5_promoter_500bpsummits.bed
bedtools slop -i output/liftover/E13.5_promoter_summits.bed -b 250 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E13.5_promoter_500bpsummits.bed
bedtools slop -i output/liftover/E14.5_promoter_summits.bed -b 250 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E14.5_promoter_500bpsummits.bed
bedtools slop -i output/liftover/E15.5_promoter_summits.bed -b 250 -g data/genomic_data/mm10.chrom.sizes > output/liftover/E15.5_promoter_500bpsummits.bed
```

### LiftOver extended peak summits
#### LiftOver dunnart peaks to mouse genome
```{bash eval=FALSE}

## Enhancer-associated peaks
liftOver output/liftover/dunnart_enhancer_50bpsummits.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_50bpsummits_smiCraTOmm10.bed output/liftover/dunnart_enhancer_50bpsummits_smiCraTOmm10_unmapped.bed

liftOver output/liftover/dunnart_enhancer_100bpsummits.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_100bpsummits_smiCraTOmm10.bed output/liftover/dunnart_enhancer_100bpsummits_smiCraTOmm10_unmapped.bed

liftOver output/liftover/dunnart_enhancer_200bpsummits.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_200bpsummits_smiCraTOmm10.bed output/liftover/dunnart_enhancer_200bpsummits_smiCraTOmm10_unmapped.bed

liftOver output/liftover/dunnart_enhancer_300bpsummits.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_300bpsummits_smiCraTOmm10.bed output/liftover/dunnart_enhancer_300bpsummits_smiCraTOmm10_unmapped.bed

liftOver output/liftover/dunnart_enhancer_400bpsummits.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_400bpsummits_smiCraTOmm10.bed output/liftover/dunnart_enhancer_400bpsummits_smiCraTOmm10_unmapped.bed

liftOver output/liftover/dunnart_enhancer_500bpsummits.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_500bpsummits_smiCraTOmm10.bed output/liftover/dunnart_enhancer_500bpsummits_smiCraTOmm10_unmapped.bed

## Promoter-associated peaks
liftOver output/liftover/dunnart_promoter_50bpsummits.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_50bpsummits_smiCraTOmm10.bed output/liftover/dunnart_promoter_50bpsummits_smiCraTOmm10_unmapped.bed

liftOver output/liftover/dunnart_promoter_100bpsummits.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_100bpsummits_smiCraTOmm10.bed output/liftover/dunnart_promoter_100bpsummits_smiCraTOmm10_unmapped.bed

liftOver output/liftover/dunnart_promoter_200bpsummits.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_200bpsummits_smiCraTOmm10.bed output/liftover/dunnart_promoter_200bpsummits_smiCraTOmm10_unmapped.bed

liftOver output/liftover/dunnart_promoter_300bpsummits.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_300bpsummits_smiCraTOmm10.bed output/liftover/dunnart_promoter_300bpsummits_smiCraTOmm10_unmapped.bed

liftOver output/liftover/dunnart_promoter_400bpsummits.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_400bpsummits_smiCraTOmm10.bed output/liftover/dunnart_promoter_400bpsummits_smiCraTOmm10_unmapped.bed

liftOver output/liftover/dunnart_promoter_500bpsummits.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_500bpsummits_smiCraTOmm10.bed output/liftover/dunnart_promoter_500bpsummits_smiCraTOmm10_unmapped.bed
```

#### Lift back to the dunnart genome
```{bash eval=FALSE}
## Enhancer-associated peaks
liftOver output/liftover/dunnart_enhancer_50bpsummits_smiCraTOmm10.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_unmapped.bed

liftOver output/liftover/dunnart_enhancer_100bpsummits_smiCraTOmm10.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/liftover/dunnart_enhancer_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_unmapped.bed

liftOver output/liftover/dunnart_enhancer_200bpsummits_smiCraTOmm10.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/liftover/dunnart_enhancer_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_unmapped.bed

liftOver output/liftover/dunnart_enhancer_300bpsummits_smiCraTOmm10.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/liftover/dunnart_enhancer_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_unmapped.bed

liftOver output/liftover/dunnart_enhancer_400bpsummits_smiCraTOmm10.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/liftover/dunnart_enhancer_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_unmapped.bed

liftOver output/liftover/dunnart_enhancer_500bpsummits_smiCraTOmm10.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/liftover/dunnart_enhancer_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_unmapped.bed

## Promoter-associated peaks
liftOver output/liftover/dunnart_promoter_50bpsummits_smiCraTOmm10.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_unmapped.bed

liftOver output/liftover/dunnart_promoter_100bpsummits_smiCraTOmm10.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/liftover/dunnart_promoter_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_unmapped.bed

liftOver output/liftover/dunnart_promoter_200bpsummits_smiCraTOmm10.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/liftover/dunnart_promoter_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_unmapped.bed

liftOver output/liftover/dunnart_promoter_300bpsummits_smiCraTOmm10.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/liftover/dunnart_promoter_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_unmapped.bed

liftOver output/liftover/dunnart_promoter_400bpsummits_smiCraTOmm10.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/liftover/dunnart_promoter_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_unmapped.bed

liftOver output/liftover/dunnart_promoter_500bpsummits_smiCraTOmm10.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/liftover/dunnart_promoter_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_unmapped.bed
```


#### Lift back to mouse genome so that everything is in mouse coordinates
```{bash eval=FALSE}
## Enhancer-assocaited peaks
liftOver output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10_unmapped.bed

liftOver output/liftover/dunnart_enhancer_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed output/liftover/dunnart_enhancer_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10_unmapped.bed

liftOver output/liftover/dunnart_enhancer_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed output/liftover/dunnart_enhancer_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10_unmapped.bed

liftOver output/liftover/dunnart_enhancer_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed output/liftover/dunnart_enhancer_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10_unmapped.bed

liftOver output/liftover/dunnart_enhancer_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed output/liftover/dunnart_enhancer_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10_unmapped.bed

liftOver output/liftover/dunnart_enhancer_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed output/liftover/dunnart_enhancer_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10_unmapped.bed

## Promoter-associated peaks 
liftOver output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10_unmapped.bed

liftOver output/liftover/dunnart_promoter_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed output/liftover/dunnart_promoter_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10_unmapped.bed

liftOver output/liftover/dunnart_promoter_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed output/liftover/dunnart_promoter_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10_unmapped.bed

liftOver output/liftover/dunnart_promoter_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed output/liftover/dunnart_promoter_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10_unmapped.bed

liftOver output/liftover/dunnart_promoter_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed output/liftover/dunnart_promoter_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10_unmapped.bed

liftOver output/liftover/dunnart_promoter_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed output/liftover/dunnart_promoter_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10_unmapped.bed

```

### Intersect dunnart CREs with mouse CREs
```{bash eval=FALSE}
## Promoter-associated peaks
bedtools intersect -a output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E10_cluster1_peaks.narrowPeak -wo > output/liftover/E10.5_mm10intersect_dunnart_promoter_50bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E11_cluster1_peaks.narrowPeak -wo > output/liftover/E11.5_mm10intersect_dunnart_promoter_50bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E12_cluster1_peaks.narrowPeak -wo > output/liftover/E12.5_mm10intersect_dunnart_promoter_50bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E13_cluster1_peaks.narrowPeak -wo > output/liftover/E13.5_mm10intersect_dunnart_promoter_50bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E14_cluster1_peaks.narrowPeak -wo > output/liftover/E14.5_mm10intersect_dunnart_promoter_50bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E15_cluster1_peaks.narrowPeak -wo > output/liftover/E15.5_mm10intersect_dunnart_promoter_50bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E10_cluster1_peaks.narrowPeak -wo > output/liftover/E10.5_mm10intersect_dunnart_promoter_100bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E11_cluster1_peaks.narrowPeak -wo > output/liftover/E11.5_mm10intersect_dunnart_promoter_100bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E12_cluster1_peaks.narrowPeak -wo > output/liftover/E12.5_mm10intersect_dunnart_promoter_100bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E13_cluster1_peaks.narrowPeak -wo > output/liftover/E13.5_mm10intersect_dunnart_promoter_100bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E14_cluster1_peaks.narrowPeak -wo > output/liftover/E14.5_mm10intersect_dunnart_promoter_100bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E15_cluster1_peaks.narrowPeak -wo > output/liftover/E15.5_mm10intersect_dunnart_promoter_100bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E10_cluster1_peaks.narrowPeak -wo > output/liftover/E10.5_mm10intersect_dunnart_promoter_200bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E11_cluster1_peaks.narrowPeak -wo > output/liftover/E11.5_mm10intersect_dunnart_promoter_200bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E12_cluster1_peaks.narrowPeak -wo > output/liftover/E12.5_mm10intersect_dunnart_promoter_200bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E13_cluster1_peaks.narrowPeak -wo > output/liftover/E13.5_mm10intersect_dunnart_promoter_200bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E14_cluster1_peaks.narrowPeak -wo > output/liftover/E14.5_mm10intersect_dunnart_promoter_200bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E15_cluster1_peaks.narrowPeak -wo > output/liftover/E15.5_mm10intersect_dunnart_promoter_200bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E10_cluster1_peaks.narrowPeak -wo > output/liftover/E10.5_mm10intersect_dunnart_promoter_300bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E11_cluster1_peaks.narrowPeak -wo > output/liftover/E11.5_mm10intersect_dunnart_promoter_300bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E12_cluster1_peaks.narrowPeak -wo > output/liftover/E12.5_mm10intersect_dunnart_promoter_300bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E13_cluster1_peaks.narrowPeak -wo > output/liftover/E13.5_mm10intersect_dunnart_promoter_300bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E14_cluster1_peaks.narrowPeak -wo > output/liftover/E14.5_mm10intersect_dunnart_promoter_300bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E15_cluster1_peaks.narrowPeak -wo > output/liftover/E15.5_mm10intersect_dunnart_promoter_300bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E10_cluster1_peaks.narrowPeak -wo > output/liftover/E10.5_mm10intersect_dunnart_promoter_400bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E11_cluster1_peaks.narrowPeak -wo > output/liftover/E11.5_mm10intersect_dunnart_promoter_400bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E12_cluster1_peaks.narrowPeak -wo > output/liftover/E12.5_mm10intersect_dunnart_promoter_400bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E13_cluster1_peaks.narrowPeak -wo > output/liftover/E13.5_mm10intersect_dunnart_promoter_400bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E14_cluster1_peaks.narrowPeak -wo > output/liftover/E14.5_mm10intersect_dunnart_promoter_400bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E15_cluster1_peaks.narrowPeak -wo > output/liftover/E15.5_mm10intersect_dunnart_promoter_400bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E10_cluster1_peaks.narrowPeak -wo > output/liftover/E10.5_mm10intersect_dunnart_promoter_500bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E11_cluster1_peaks.narrowPeak -wo > output/liftover/E11.5_mm10intersect_dunnart_promoter_500bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E12_cluster1_peaks.narrowPeak -wo > output/liftover/E12.5_mm10intersect_dunnart_promoter_500bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E13_cluster1_peaks.narrowPeak -wo > output/liftover/E13.5_mm10intersect_dunnart_promoter_500bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E14_cluster1_peaks.narrowPeak -wo > output/liftover/E14.5_mm10intersect_dunnart_promoter_500bpsummits.bed

bedtools intersect -a output/liftover/dunnart_promoter_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E15_cluster1_peaks.narrowPeak -wo > output/liftover/E15.5_mm10intersect_dunnart_promoter_500bpsummits.bed

## Enhancer-associated peaks
bedtools intersect -a output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E10.5_enhancer_peaks.narrowPeak -wo > output/liftover/E10.5_mm10intersect_dunnart_enhancer_50bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E11.5_enhancer_peaks.narrowPeak -wo > output/liftover/E11.5_mm10intersect_dunnart_enhancer_50bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E12.5_enhancer_peaks.narrowPeak -wo > output/liftover/E12.5_mm10intersect_dunnart_enhancer_50bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E13.5_enhancer_peaks.narrowPeak -wo > output/liftover/E13.5_mm10intersect_dunnart_enhancer_50bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E14.5_enhancer_peaks.narrowPeak -wo > output/liftover/E14.5_mm10intersect_dunnart_enhancer_50bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E15.5_enhancer_peaks.narrowPeak -wo > output/liftover/E15.5_mm10intersect_dunnart_enhancer_50bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E10.5_enhancer_peaks.narrowPeak -wo > output/liftover/E10.5_mm10intersect_dunnart_enhancer_100bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E11.5_enhancer_peaks.narrowPeak -wo > output/liftover/E11.5_mm10intersect_dunnart_enhancer_100bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E12.5_enhancer_peaks.narrowPeak -wo > output/liftover/E12.5_mm10intersect_dunnart_enhancer_100bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E13.5_enhancer_peaks.narrowPeak -wo > output/liftover/E13.5_mm10intersect_dunnart_enhancer_100bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E14.5_enhancer_peaks.narrowPeak -wo > output/liftover/E14.5_mm10intersect_dunnart_enhancer_100bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_100bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E15.5_enhancer_peaks.narrowPeak -wo > output/liftover/E15.5_mm10intersect_dunnart_enhancer_100bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E10.5_enhancer_peaks.narrowPeak -wo > output/liftover/E10.5_mm10intersect_dunnart_enhancer_200bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E11.5_enhancer_peaks.narrowPeak -wo > output/liftover/E11.5_mm10intersect_dunnart_enhancer_200bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E12.5_enhancer_peaks.narrowPeak -wo > output/liftover/E12.5_mm10intersect_dunnart_enhancer_200bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E13.5_enhancer_peaks.narrowPeak -wo > output/liftover/E13.5_mm10intersect_dunnart_enhancer_200bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E14.5_enhancer_peaks.narrowPeak -wo > output/liftover/E14.5_mm10intersect_dunnart_enhancer_200bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_200bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E15.5_enhancer_peaks.narrowPeak -wo > output/liftover/E15.5_mm10intersect_dunnart_enhancer_200bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E10.5_enhancer_peaks.narrowPeak -wo > output/liftover/E10.5_mm10intersect_dunnart_enhancer_300bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E11.5_enhancer_peaks.narrowPeak -wo > output/liftover/E11.5_mm10intersect_dunnart_enhancer_300bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E12.5_enhancer_peaks.narrowPeak -wo > output/liftover/E12.5_mm10intersect_dunnart_enhancer_300bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E13.5_enhancer_peaks.narrowPeak -wo > output/liftover/E13.5_mm10intersect_dunnart_enhancer_300bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E14.5_enhancer_peaks.narrowPeak -wo > output/liftover/E14.5_mm10intersect_dunnart_enhancer_300bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_300bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E15.5_enhancer_peaks.narrowPeak -wo > output/liftover/E15.5_mm10intersect_dunnart_enhancer_300bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E10.5_enhancer_peaks.narrowPeak -wo > output/liftover/E10.5_mm10intersect_dunnart_enhancer_400bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E11.5_enhancer_peaks.narrowPeak -wo > output/liftover/E11.5_mm10intersect_dunnart_enhancer_400bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E12.5_enhancer_peaks.narrowPeak -wo > output/liftover/E12.5_mm10intersect_dunnart_enhancer_400bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E13.5_enhancer_peaks.narrowPeak -wo > output/liftover/E13.5_mm10intersect_dunnart_enhancer_400bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E14.5_enhancer_peaks.narrowPeak -wo > output/liftover/E14.5_mm10intersect_dunnart_enhancer_400bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_400bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E15.5_enhancer_peaks.narrowPeak -wo > output/liftover/E15.5_mm10intersect_dunnart_enhancer_400bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E10.5_enhancer_peaks.narrowPeak -wo > output/liftover/E10.5_mm10intersect_dunnart_enhancer_500bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E11.5_enhancer_peaks.narrowPeak -wo > output/liftover/E11.5_mm10intersect_dunnart_enhancer_500bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E12.5_enhancer_peaks.narrowPeak -wo > output/liftover/E12.5_mm10intersect_dunnart_enhancer_500bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E13.5_enhancer_peaks.narrowPeak -wo > output/liftover/E13.5_mm10intersect_dunnart_enhancer_500bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E14.5_enhancer_peaks.narrowPeak -wo > output/liftover/E14.5_mm10intersect_dunnart_enhancer_500bpsummits.bed

bedtools intersect -a output/liftover/dunnart_enhancer_500bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E15.5_enhancer_peaks.narrowPeak -wo > output/liftover/E15.5_mm10intersect_dunnart_enhancer_500bpsummits.bed
```



### Use window to allow intersections within 50 bps 
```{bash eval=FALSE}
bedtools window -w 50 -u -a output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E10_cluster1_peaks.narrowPeak  > output/liftover/E10.5_mm10intersect_dunnart_promoter_50bpsummits_window.bed
bedtools window -w 50 -u -a output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E11_cluster1_peaks.narrowPeak  > output/liftover/E11.5_mm10intersect_dunnart_promoter_50bpsummits_window.bed
bedtools window -w 50 -u -a output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E12_cluster1_peaks.narrowPeak  > output/liftover/E12.5_mm10intersect_dunnart_promoter_50bpsummits_window.bed
bedtools window -w 50 -u -a output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E13_cluster1_peaks.narrowPeak  > output/liftover/E13.5_mm10intersect_dunnart_promoter_50bpsummits_window.bed
bedtools window -w 50 -u -a output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E14_cluster1_peaks.narrowPeak  > output/liftover/E14.5_mm10intersect_dunnart_promoter_50bpsummits_window.bed
bedtools window -w 50 -u -a output/liftover/dunnart_promoter_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/filtered_peaks/E15_cluster1_peaks.narrowPeak  > output/liftover/E15.5_mm10intersect_dunnart_promoter_50bpsummits_window.bed

bedtools window -w 50 -u -a output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E10.5_enhancer_peaks.narrowPeak  > output/liftover/E10.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed
bedtools window -w 50 -u -a output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E11.5_enhancer_peaks.narrowPeak  > output/liftover/E11.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed
bedtools window -w 50 -u -a output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E12.5_enhancer_peaks.narrowPeak  > output/liftover/E12.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed
bedtools window -w 50 -u -a output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E13.5_enhancer_peaks.narrowPeak  > output/liftover/E13.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed
bedtools window -w 50 -u -a output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E14.5_enhancer_peaks.narrowPeak  > output/liftover/E14.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed
bedtools window -w 50 -u -a output/liftover/dunnart_enhancer_50bpsummits.bed_smiCraTOmm10_mm10TOsmiCra_backTOmm10.bed -b output/peaks/E15.5_enhancer_peaks.narrowPeak  > output/liftover/E15.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed
```

#### Lift dunnart peaks back over to the dunnart genome

```{bash eval=FALSE}
liftOver -bedPlus=4 output/liftover/E10.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/E10.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra.bed output/liftover/E10.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra_unmapped.bed

liftOver -bedPlus=4 output/liftover/E11.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/E11.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra.bed output/liftover/E11.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra_unmapped.bed

liftOver -bedPlus=4 output/liftover/E12.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/E12.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra.bed output/liftover/E12.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra_unmapped.bed

liftOver -bedPlus=4 output/liftover/E13.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/E13.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra.bed output/liftover/E13.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra_unmapped.bed

liftOver -bedPlus=4 output/liftover/E14.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/E14.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra.bed output/liftover/E14.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra_unmapped.bed

liftOver -bedPlus=4 output/liftover/E15.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/E15.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra.bed output/liftover/E15.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra_unmapped.bed

liftOver -bedPlus=4 output/liftover/E10.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/E10.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra.bed output/liftover/E10.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra_unmapped.bed

liftOver -bedPlus=4 output/liftover/E11.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/E11.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra.bed output/liftover/E11.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra_unmapped.bed

liftOver -bedPlus=4 output/liftover/E12.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/E12.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra.bed output/liftover/E12.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra_unmapped.bed

liftOver -bedPlus=4 output/liftover/E13.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/E13.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra.bed output/liftover/E13.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra_unmapped.bed

liftOver -bedPlus=4 output/liftover/E14.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/E14.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra.bed output/liftover/E14.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra_unmapped.bed

liftOver -bedPlus=4 output/liftover/E15.5_mm10intersect_dunnart_enhancer_50bpsummits_window.bed output/wga/liftOver_chains/mm10TOsmiCra1_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/E15.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra.bed output/liftover/E15.5_mm10intersect_dunnart_enhancer_50bpsummits_window_backTOsmiCra_unmapped.bed

```

## When you lift over a peak from one species to another, does it always land next to the same gene in both species?
Use annotated peak files for all peaks and compare nearest gene call

### Intersect annotation file with peak summits

```{bash eval=FALSE}
bedtools intersect -a output/liftover/dunnart_promoter_50bpsummits.bed -b output/annotations/dunnart_promoter_cluster1_annotationConvertedIDs.bed -wb > output/liftover/dunnart_promoter_50bpsummits_annotation.bed

bedtools intersect -a output/liftover/dunnart_enhancer_50bpsummits.bed -b output/annotations/dunnart_enhancer_annotationConvertedIDs.bed -wb > output/liftover/dunnart_enhancer_50bpsummits_annotation.bed

bedtools intersect -a output/liftover/E10.5_promoter_50bpsummits.bed -b output/annotations/E10_cluster1_annotation.bed -wb > output/liftover/E10_promoter_50bpsummits_annotation.bed
bedtools intersect -a output/liftover/E11.5_promoter_50bpsummits.bed -b output/annotations/E11_cluster1_annotation.bed -wb > output/liftover/E11_promoter_50bpsummits_annotation.bed
bedtools intersect -a output/liftover/E12.5_promoter_50bpsummits.bed -b output/annotations/E12_cluster1_annotation.bed -wb > output/liftover/E12_promoter_50bpsummits_annotation.bed
bedtools intersect -a output/liftover/E13.5_promoter_50bpsummits.bed -b output/annotations/E13_cluster1_annotation.bed -wb > output/liftover/E13_promoter_50bpsummits_annotation.bed
bedtools intersect -a output/liftover/E14.5_promoter_50bpsummits.bed -b output/annotations/E14_cluster1_annotation.bed -wb > output/liftover/E14_promoter_50bpsummits_annotation.bed
bedtools intersect -a output/liftover/E15.5_promoter_50bpsummits.bed -b output/annotations/E15_cluster1_annotation.bed -wb > output/liftover/E15_promoter_50bpsummits_annotation.bed

bedtools intersect -a output/liftover/E10.5_enhancer_50bpsummits.bed -b output/annotations/E10.5_enhancer_annotation.bed -wb > output/liftover/E10_enhancer_50bpsummits_annotation.bed
bedtools intersect -a output/liftover/E11.5_enhancer_50bpsummits.bed -b output/annotations/E11.5_enhancer_annotation.bed -wb > output/liftover/E11_enhancer_50bpsummits_annotation.bed
bedtools intersect -a output/liftover/E12.5_enhancer_50bpsummits.bed -b output/annotations/E12.5_enhancer_annotation.bed -wb > output/liftover/E12_enhancer_50bpsummits_annotation.bed
bedtools intersect -a output/liftover/E13.5_enhancer_50bpsummits.bed -b output/annotations/E13.5_enhancer_annotation.bed -wb > output/liftover/E13_enhancer_50bpsummits_annotation.bed
bedtools intersect -a output/liftover/E14.5_enhancer_50bpsummits.bed -b output/annotations/E14.5_enhancer_annotation.bed -wb > output/liftover/E14_enhancer_50bpsummits_annotation.bed
bedtools intersect -a output/liftover/E15.5_enhancer_50bpsummits.bed -b output/annotations/E15.5_enhancer_annotation.bed -wb > output/liftover/E15_enhancer_50bpsummits_annotation.bed

bedtools intersect -a output/liftover/dunnart_promoter_100bpsummits.bed -b output/annotations/dunnart_promoter_cluster1_annotationConvertedIDs.bed -wb > output/liftover/dunnart_promoter_100bpsummits_annotation.bed

bedtools intersect -a output/liftover/dunnart_enhancer_100bpsummits.bed -b output/annotations/dunnart_enhancer_annotationConvertedIDs.bed -wb > output/liftover/dunnart_enhancer_100bpsummits_annotation.bed

bedtools intersect -a output/liftover/E10.5_promoter_100bpsummits.bed -b output/annotations/E10_cluster1_annotation.bed -wb > output/liftover/E10_promoter_100bpsummits_annotation.bed
bedtools intersect -a output/liftover/E11.5_promoter_100bpsummits.bed -b output/annotations/E11_cluster1_annotation.bed -wb > output/liftover/E11_promoter_100bpsummits_annotation.bed
bedtools intersect -a output/liftover/E12.5_promoter_100bpsummits.bed -b output/annotations/E12_cluster1_annotation.bed -wb > output/liftover/E12_promoter_100bpsummits_annotation.bed
bedtools intersect -a output/liftover/E13.5_promoter_100bpsummits.bed -b output/annotations/E13_cluster1_annotation.bed -wb > output/liftover/E13_promoter_100bpsummits_annotation.bed
bedtools intersect -a output/liftover/E14.5_promoter_100bpsummits.bed -b output/annotations/E14_cluster1_annotation.bed -wb > output/liftover/E14_promoter_100bpsummits_annotation.bed
bedtools intersect -a output/liftover/E15.5_promoter_100bpsummits.bed -b output/annotations/E15_cluster1_annotation.bed -wb > output/liftover/E15_promoter_100bpsummits_annotation.bed

bedtools intersect -a output/liftover/E10.5_enhancer_100bpsummits.bed -b output/annotations/E10.5_enhancer_annotation.bed -wb > output/liftover/E10_enhancer_100bpsummits_annotation.bed
bedtools intersect -a output/liftover/E11.5_enhancer_100bpsummits.bed -b output/annotations/E11.5_enhancer_annotation.bed -wb > output/liftover/E11_enhancer_100bpsummits_annotation.bed
bedtools intersect -a output/liftover/E12.5_enhancer_100bpsummits.bed -b output/annotations/E12.5_enhancer_annotation.bed -wb > output/liftover/E12_enhancer_100bpsummits_annotation.bed
bedtools intersect -a output/liftover/E13.5_enhancer_100bpsummits.bed -b output/annotations/E13.5_enhancer_annotation.bed -wb > output/liftover/E13_enhancer_100bpsummits_annotation.bed
bedtools intersect -a output/liftover/E14.5_enhancer_100bpsummits.bed -b output/annotations/E14.5_enhancer_annotation.bed -wb > output/liftover/E14_enhancer_100bpsummits_annotation.bed
bedtools intersect -a output/liftover/E15.5_enhancer_100bpsummits.bed -b output/annotations/E15.5_enhancer_annotation.bed -wb > output/liftover/E15_enhancer_100bpsummits_annotation.bed

bedtools intersect -a output/liftover/dunnart_promoter_200bpsummits.bed -b output/annotations/dunnart_promoter_cluster1_annotationConvertedIDs.bed -wb > output/liftover/dunnart_promoter_200bpsummits_annotation.bed

bedtools intersect -a output/liftover/dunnart_enhancer_200bpsummits.bed -b output/annotations/dunnart_enhancer_annotationConvertedIDs.bed -wb > output/liftover/dunnart_enhancer_200bpsummits_annotation.bed

bedtools intersect -a output/liftover/E10.5_promoter_200bpsummits.bed -b output/annotations/E10_cluster1_annotation.bed -wb > output/liftover/E10_promoter_200bpsummits_annotation.bed
bedtools intersect -a output/liftover/E11.5_promoter_200bpsummits.bed -b output/annotations/E11_cluster1_annotation.bed -wb > output/liftover/E11_promoter_200bpsummits_annotation.bed
bedtools intersect -a output/liftover/E12.5_promoter_200bpsummits.bed -b output/annotations/E12_cluster1_annotation.bed -wb > output/liftover/E12_promoter_200bpsummits_annotation.bed
bedtools intersect -a output/liftover/E13.5_promoter_200bpsummits.bed -b output/annotations/E13_cluster1_annotation.bed -wb > output/liftover/E13_promoter_200bpsummits_annotation.bed
bedtools intersect -a output/liftover/E14.5_promoter_200bpsummits.bed -b output/annotations/E14_cluster1_annotation.bed -wb > output/liftover/E14_promoter_200bpsummits_annotation.bed
bedtools intersect -a output/liftover/E15.5_promoter_200bpsummits.bed -b output/annotations/E15_cluster1_annotation.bed -wb > output/liftover/E15_promoter_200bpsummits_annotation.bed

bedtools intersect -a output/liftover/E10.5_enhancer_200bpsummits.bed -b output/annotations/E10.5_enhancer_annotation.bed -wb > output/liftover/E10_enhancer_200bpsummits_annotation.bed
bedtools intersect -a output/liftover/E11.5_enhancer_200bpsummits.bed -b output/annotations/E11.5_enhancer_annotation.bed -wb > output/liftover/E11_enhancer_200bpsummits_annotation.bed
bedtools intersect -a output/liftover/E12.5_enhancer_200bpsummits.bed -b output/annotations/E12.5_enhancer_annotation.bed -wb > output/liftover/E12_enhancer_200bpsummits_annotation.bed
bedtools intersect -a output/liftover/E13.5_enhancer_200bpsummits.bed -b output/annotations/E13.5_enhancer_annotation.bed -wb > output/liftover/E13_enhancer_200bpsummits_annotation.bed
bedtools intersect -a output/liftover/E14.5_enhancer_200bpsummits.bed -b output/annotations/E14.5_enhancer_annotation.bed -wb > output/liftover/E14_enhancer_200bpsummits_annotation.bed
bedtools intersect -a output/liftover/E15.5_enhancer_200bpsummits.bed -b output/annotations/E15.5_enhancer_annotation.bed -wb > output/liftover/E15_enhancer_200bpsummits_annotation.bed

bedtools intersect -a output/liftover/dunnart_promoter_300bpsummits.bed -b output/annotations/dunnart_promoter_cluster1_annotationConvertedIDs.bed -wb > output/liftover/dunnart_promoter_300bpsummits_annotation.bed

bedtools intersect -a output/liftover/dunnart_enhancer_300bpsummits.bed -b output/annotations/dunnart_enhancer_annotationConvertedIDs.bed -wb > output/liftover/dunnart_enhancer_300bpsummits_annotation.bed

bedtools intersect -a output/liftover/E10.5_promoter_300bpsummits.bed -b output/annotations/E10_cluster1_annotation.bed -wb > output/liftover/E10_promoter_300bpsummits_annotation.bed
bedtools intersect -a output/liftover/E11.5_promoter_300bpsummits.bed -b output/annotations/E11_cluster1_annotation.bed -wb > output/liftover/E11_promoter_300bpsummits_annotation.bed
bedtools intersect -a output/liftover/E12.5_promoter_300bpsummits.bed -b output/annotations/E12_cluster1_annotation.bed -wb > output/liftover/E12_promoter_300bpsummits_annotation.bed
bedtools intersect -a output/liftover/E13.5_promoter_300bpsummits.bed -b output/annotations/E13_cluster1_annotation.bed -wb > output/liftover/E13_promoter_300bpsummits_annotation.bed
bedtools intersect -a output/liftover/E14.5_promoter_300bpsummits.bed -b output/annotations/E14_cluster1_annotation.bed -wb > output/liftover/E14_promoter_300bpsummits_annotation.bed
bedtools intersect -a output/liftover/E15.5_promoter_300bpsummits.bed -b output/annotations/E15_cluster1_annotation.bed -wb > output/liftover/E15_promoter_300bpsummits_annotation.bed

bedtools intersect -a output/liftover/E10.5_enhancer_300bpsummits.bed -b output/annotations/E10.5_enhancer_annotation.bed -wb > output/liftover/E10_enhancer_300bpsummits_annotation.bed
bedtools intersect -a output/liftover/E11.5_enhancer_300bpsummits.bed -b output/annotations/E11.5_enhancer_annotation.bed -wb > output/liftover/E11_enhancer_300bpsummits_annotation.bed
bedtools intersect -a output/liftover/E12.5_enhancer_300bpsummits.bed -b output/annotations/E12.5_enhancer_annotation.bed -wb > output/liftover/E12_enhancer_300bpsummits_annotation.bed
bedtools intersect -a output/liftover/E13.5_enhancer_300bpsummits.bed -b output/annotations/E13.5_enhancer_annotation.bed -wb > output/liftover/E13_enhancer_300bpsummits_annotation.bed
bedtools intersect -a output/liftover/E14.5_enhancer_300bpsummits.bed -b output/annotations/E14.5_enhancer_annotation.bed -wb > output/liftover/E14_enhancer_300bpsummits_annotation.bed
bedtools intersect -a output/liftover/E15.5_enhancer_300bpsummits.bed -b output/annotations/E15.5_enhancer_annotation.bed -wb > output/liftover/E15_enhancer_300bpsummits_annotation.bed

bedtools intersect -a output/liftover/dunnart_promoter_400bpsummits.bed -b output/annotations/dunnart_promoter_cluster1_annotationConvertedIDs.bed -wb > output/liftover/dunnart_promoter_400bpsummits_annotation.bed

bedtools intersect -a output/liftover/dunnart_enhancer_400bpsummits.bed -b output/annotations/dunnart_enhancer_annotationConvertedIDs.bed -wb > output/liftover/dunnart_enhancer_400bpsummits_annotation.bed

bedtools intersect -a output/liftover/E10.5_promoter_400bpsummits.bed -b output/annotations/E10_cluster1_annotation.bed -wb > output/liftover/E10_promoter_400bpsummits_annotation.bed
bedtools intersect -a output/liftover/E11.5_promoter_400bpsummits.bed -b output/annotations/E11_cluster1_annotation.bed -wb > output/liftover/E11_promoter_400bpsummits_annotation.bed
bedtools intersect -a output/liftover/E12.5_promoter_400bpsummits.bed -b output/annotations/E12_cluster1_annotation.bed -wb > output/liftover/E12_promoter_400bpsummits_annotation.bed
bedtools intersect -a output/liftover/E13.5_promoter_400bpsummits.bed -b output/annotations/E13_cluster1_annotation.bed -wb > output/liftover/E13_promoter_400bpsummits_annotation.bed
bedtools intersect -a output/liftover/E14.5_promoter_400bpsummits.bed -b output/annotations/E14_cluster1_annotation.bed -wb > output/liftover/E14_promoter_400bpsummits_annotation.bed
bedtools intersect -a output/liftover/E15.5_promoter_400bpsummits.bed -b output/annotations/E15_cluster1_annotation.bed -wb > output/liftover/E15_promoter_400bpsummits_annotation.bed

bedtools intersect -a output/liftover/E10.5_enhancer_400bpsummits.bed -b output/annotations/E10.5_enhancer_annotation.bed -wb > output/liftover/E10_enhancer_400bpsummits_annotation.bed
bedtools intersect -a output/liftover/E11.5_enhancer_400bpsummits.bed -b output/annotations/E11.5_enhancer_annotation.bed -wb > output/liftover/E11_enhancer_400bpsummits_annotation.bed
bedtools intersect -a output/liftover/E12.5_enhancer_400bpsummits.bed -b output/annotations/E12.5_enhancer_annotation.bed -wb > output/liftover/E12_enhancer_400bpsummits_annotation.bed
bedtools intersect -a output/liftover/E13.5_enhancer_400bpsummits.bed -b output/annotations/E13.5_enhancer_annotation.bed -wb > output/liftover/E13_enhancer_400bpsummits_annotation.bed
bedtools intersect -a output/liftover/E14.5_enhancer_400bpsummits.bed -b output/annotations/E14.5_enhancer_annotation.bed -wb > output/liftover/E14_enhancer_400bpsummits_annotation.bed
bedtools intersect -a output/liftover/E15.5_enhancer_400bpsummits.bed -b output/annotations/E15.5_enhancer_annotation.bed -wb > output/liftover/E15_enhancer_400bpsummits_annotation.bed

bedtools intersect -a output/liftover/dunnart_promoter_500bpsummits.bed -b output/annotations/dunnart_promoter_cluster1_annotationConvertedIDs.bed -wb > output/liftover/dunnart_promoter_500bpsummits_annotation.bed

bedtools intersect -a output/liftover/dunnart_enhancer_500bpsummits.bed -b output/annotations/dunnart_enhancer_annotationConvertedIDs.bed -wb > output/liftover/dunnart_enhancer_500bpsummits_annotation.bed

bedtools intersect -a output/liftover/E10.5_promoter_500bpsummits.bed -b output/annotations/E10_cluster1_annotation.bed -wb > output/liftover/E10_promoter_500bpsummits_annotation.bed
bedtools intersect -a output/liftover/E11.5_promoter_500bpsummits.bed -b output/annotations/E11_cluster1_annotation.bed -wb > output/liftover/E11_promoter_500bpsummits_annotation.bed
bedtools intersect -a output/liftover/E12.5_promoter_500bpsummits.bed -b output/annotations/E12_cluster1_annotation.bed -wb > output/liftover/E12_promoter_500bpsummits_annotation.bed
bedtools intersect -a output/liftover/E13.5_promoter_500bpsummits.bed -b output/annotations/E13_cluster1_annotation.bed -wb > output/liftover/E13_promoter_500bpsummits_annotation.bed
bedtools intersect -a output/liftover/E14.5_promoter_500bpsummits.bed -b output/annotations/E14_cluster1_annotation.bed -wb > output/liftover/E14_promoter_500bpsummits_annotation.bed
bedtools intersect -a output/liftover/E15.5_promoter_500bpsummits.bed -b output/annotations/E15_cluster1_annotation.bed -wb > output/liftover/E15_promoter_500bpsummits_annotation.bed

bedtools intersect -a output/liftover/E10.5_enhancer_500bpsummits.bed -b output/annotations/E10.5_enhancer_annotation.bed -wb > output/liftover/E10_enhancer_500bpsummits_annotation.bed
bedtools intersect -a output/liftover/E11.5_enhancer_500bpsummits.bed -b output/annotations/E11.5_enhancer_annotation.bed -wb > output/liftover/E11_enhancer_500bpsummits_annotation.bed
bedtools intersect -a output/liftover/E12.5_enhancer_500bpsummits.bed -b output/annotations/E12.5_enhancer_annotation.bed -wb > output/liftover/E12_enhancer_500bpsummits_annotation.bed
bedtools intersect -a output/liftover/E13.5_enhancer_500bpsummits.bed -b output/annotations/E13.5_enhancer_annotation.bed -wb > output/liftover/E13_enhancer_500bpsummits_annotation.bed
bedtools intersect -a output/liftover/E14.5_enhancer_500bpsummits.bed -b output/annotations/E14.5_enhancer_annotation.bed -wb > output/liftover/E14_enhancer_500bpsummits_annotation.bed
bedtools intersect -a output/liftover/E15.5_enhancer_500bpsummits.bed -b output/annotations/E15.5_enhancer_annotation.bed -wb > output/liftover/E15_enhancer_500bpsummits_annotation.bed
```


### Liftover dunnart peaks with annotation to mouse
```{bash eval=FALSE}
liftOver -bedPlus=4 output/liftover/dunnart_promoter_50bpsummits_annotation.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_50bpsummits_annotation_smiCraTOmm10.bed output/liftover/dunnart_promoter_50bpsummits_annotation_smiCraTOmm10_unmapped.bed

liftOver -bedPlus=4 output/liftover/dunnart_promoter_100bpsummits_annotation.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_100bpsummits_annotation_smiCraTOmm10.bed output/liftover/dunnart_promoter_100bpsummits_annotation_smiCraTOmm10_unmapped.bed

liftOver -bedPlus=4 output/liftover/dunnart_promoter_200bpsummits_annotation.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_200bpsummits_annotation_smiCraTOmm10.bed output/liftover/dunnart_promoter_200bpsummits_annotation_smiCraTOmm10_unmapped.bed

liftOver -bedPlus=4 output/liftover/dunnart_promoter_300bpsummits_annotation.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_300bpsummits_annotation_smiCraTOmm10.bed output/liftover/dunnart_promoter_300bpsummits_annotation_smiCraTOmm10_unmapped.bed

liftOver -bedPlus=4 output/liftover/dunnart_promoter_400bpsummits_annotation.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_400bpsummits_annotation_smiCraTOmm10.bed output/liftover/dunnart_promoter_400bpsummits_annotation_smiCraTOmm10_unmapped.bed

liftOver -bedPlus=4 output/liftover/dunnart_promoter_500bpsummits_annotation.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_promoter_500bpsummits_annotation_smiCraTOmm10.bed output/liftover/dunnart_promoter_500bpsummits_annotation_smiCraTOmm10_unmapped.bed

liftOver -bedPlus=4 output/liftover/dunnart_enhancer_50bpsummits_annotation.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_50bpsummits_annotation_smiCraTOmm10.bed output/liftover/dunnart_enhancer_50bpsummits_annotation_smiCraTOmm10_unmapped.bed

liftOver -bedPlus=4 output/liftover/dunnart_enhancer_100bpsummits_annotation.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_100bpsummits_annotation_smiCraTOmm10.bed output/liftover/dunnart_enhancer_100bpsummits_annotation_smiCraTOmm10_unmapped.bed

liftOver -bedPlus=4 output/liftover/dunnart_enhancer_200bpsummits_annotation.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_200bpsummits_annotation_smiCraTOmm10.bed output/liftover/dunnart_enhancer_200bpsummits_annotation_smiCraTOmm10_unmapped.bed

liftOver -bedPlus=4 output/liftover/dunnart_enhancer_300bpsummits_annotation.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_300bpsummits_annotation_smiCraTOmm10.bed output/liftover/dunnart_enhancer_300bpsummits_annotation_smiCraTOmm10_unmapped.bed

liftOver -bedPlus=4 output/liftover/dunnart_enhancer_400bpsummits_annotation.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_400bpsummits_annotation_smiCraTOmm10.bed output/liftover/dunnart_enhancer_400bpsummits_annotation_smiCraTOmm10_unmapped.bed

liftOver -bedPlus=4 output/liftover/dunnart_enhancer_500bpsummits_annotation.bed output/wga/liftOver_chains/smiCra1TOmm10_patched_sorted_repFil_chainCl_preNet_chainNet_stitched.chain output/liftover/dunnart_enhancer_500bpsummits_annotation_smiCraTOmm10.bed output/liftover/dunnart_enhancer_500bpsummits_annotation_smiCraTOmm10_unmapped.bed
```
